Evaluating Perceptual Judgements on 3D Printed Bar Charts

### 2024-01-22 jds.rmd
Removed residual plots

Model diagnostic plots show slight violations of normality with the error term, particularly with right-skewed residuals.
Plots of the data for each ratio tend to suggest that some participants might have tried rounding to the ratio increments of fives and tens. 
For example, participants tended to favor estimating the ratio of 0.562 to around 0.5.
Since linear models are reasonably robust to violations of normality, we will assume that the model reasonably fits.
Plots of the residual diagnostics can be found under the supplemental material in \Cref{fig:residualplots}.

@@

>>>>

<!---Model diagnostic plots show slight violations of normality with the error term, particularly with right-skewed residuals.
Plots of the data for each ratio tend to suggest that some participants might have tried rounding to the ratio increments of fives and tens. 
For example, participants tended to favor estimating the ratio of 0.562 to around 0.5.
Since linear models are reasonably robust to violations of normality, we will assume that the model reasonably fits.
Plots of the residual diagnostics can be found under the supplemental material in \Cref{fig:residualplots}.--->

@@

```{r residualplots-gam, include = F}
#| fig-width: 3
#| fig-height: 3
#| fig-cap: "Residual diagnostic plots for the linear mixed model."
#| fig-subcap:
#| - Fitted vs. predicted residuals
#| - Q-Q plot
#| out-width: ".40\\linewidth"
#| fig-show: "hold"
#| layout-ncol: 2

r = residuals(gam_mod)
p = predict(gam_mod)

### 2024-01-22 jds.tex
Removed residual plots

Each graph presents two bars from the values given above where the participants are asked to judge the ratio of the smaller bar to the larger bar. The ratio of bars used by Cleveland and McGill were 17.8, 26.1, 38.3, 46.4 (twice), 56.2, 68.1 (twice), and 82.5 (twice).
The exact numeric comparisons were not disclosed, but the comparison values used in our study were subjected to the constraints of having the same ratio values and that no value was used more than twice. {\textcolor{ForestGreen}{Can we show the comparison values in a table?}}

{\textcolor{ForestGreen}{In each graph, there are two sets of five bars each, and two of the bars are marked for identification with a circle and triangle}}, {\textcolor{ForestGreen}{as in \Cref{fig:bar-types}.}}
Cleveland and McGill did not specify the random process for the heights of the eight other bars, so we used a scaled Beta distribution with parameters that limit excessive noise around the bars used for comparisons.{\textcolor{ForestGreen}{What does excessive noise mean??}}
Code to reproduce the data generation process, data underlying the plots used in this study, the rendered plots and STL files, anonymized user data, and analysis code can found be at \url{https://github.com/TWiedRW/2023-JDS-3dcharts}.

@@

\caption{\label{tab:gam-smooth}Approximate significance of smooth terms in gam model.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Smooth & edf & Ref.df & F & p-value\\
\midrule
s(Ratio):plot2dDigital & 0.0005 & 0.0009 & 0.0000 & 0.5000\\
s(Ratio):plot3dDigital & 1.7934 & 2.2056 & 1.2807 & 0.2481\\
s(Ratio):plot3dPrint & 1.0003 & 1.0005 & 2.4488 & 0.1183\\
s(Ratio):typeSeparated & 4.2371 & 4.7338 & 5.8074 & 0.0001\\
s(Ratio):typeAdjacent & 1.0007 & 1.0014 & 3.5452 & 0.0604\\
\addlinespace
s(participant) & 27.0449 & 34.0000 & 4.7264 & 0.0000\\
\bottomrule
\end{tabular}
\end{table}

@@

Model diagnostic plots show slight violations of normality with the error term, particularly with right-skewed residuals.
Plots of the data for each ratio tend to suggest that some participants might have tried rounding to the ratio increments of fives and tens.
For example, participants tended to favor estimating the ratio of 0.562 to around 0.5.
Since linear models are reasonably robust to violations of normality, we will assume that the model reasonably fits.
Plots of the residual diagnostics can be found under the supplemental material in \Cref{fig:residualplots}.

>>>>

Each graph presents two bars from the values given above where the participants are asked to judge the ratio of the smaller bar to the larger bar. The ratio of bars used by Cleveland and McGill were 17.8, 26.1, 38.3, 46.4 (twice), 56.2, 68.1 (twice), and 82.5 (twice).
The exact numeric comparisons were not disclosed, but the comparison values used in our study were subjected to the constraints of having the same ratio values and that no value was used more than twice.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:experiment-values}Values used in the experiment to make ratio comparisons, sorted by ratio. The ID label corresponds to the file reference number.}

\begin{tabular}{llllllll}
\toprule
Bar & \multicolumn{1}{c}{ID: 01} & \multicolumn{1}{c}{ID: 06} & \multicolumn{1}{c}{ID: 05} & \multicolumn{1}{c}{ID: 04} & \multicolumn{1}{c}{ID: 02} & \multicolumn{1}{c}{ID: 03} & \multicolumn{1}{c}{ID: 09}\\
\midrule
Smaller & 10.00 & 14.70 & 14.70 & 12.10 & 10.00 & 12.10 & 26.10\\
Larger & 56.20 & 56.20 & 38.30 & 26.10 & 17.80 & 17.80 & 31.60\\
Ratio (\%) & 17.80 & 26.20 & 38.40 & 46.40 & 56.20 & 68.00 & 82.60\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

In each graph, there are two sets of five bars each, and two of the bars are marked for identification with a circle and triangle, as in \Cref{fig:bar-types}.
Cleveland and McGill did not specify the random process for the heights of the eight other bars, so we used a scaled Beta distribution to provide random structure around our fixed values.
Code to reproduce the data generation process, data underlying the plots used in this study, the rendered plots and STL files, anonymized user data, and analysis code can found be at \url{https://github.com/TWiedRW/2023-JDS-3dcharts}.

@@

\caption{\label{tab:gam-smooth}Approximate significance of smooth terms in gam model.}
\centering
\begin{tabular}[t]{lrrrr}
\toprule
Smooth & edf & Ref.df & F & p-value\\
\midrule
s(Ratio):plot2dDigital & 0.0005 & 0.0009 & 0.0000 & 0.5000\\
s(Ratio):plot3dDigital & 1.7934 & 2.2056 & 1.2807 & 0.2481\\
s(Ratio):plot3dPrint & 1.0003 & 1.0005 & 2.4488 & 0.1183\\
s(Ratio):typeSeparated & 4.2371 & 4.7338 & 5.8074 & 0.0001\\
s(Ratio):typeAdjacent & 1.0007 & 1.0014 & 3.5452 & 0.0604\\
\addlinespace
s(participant) & 27.0449 & 34.0000 & 4.7276 & 0.0000\\
\bottomrule
\end{tabular}
\end{table}

@@
